\thispagestyle{plain}
\section*{Acknowledgements}

I would like to thank my supervisor Dr. Nelly Montcoudiol, Federal Institute for Geosciences and Natural Resources (BGR), for the constant support and the valuable hints and advices throughout the work on this master thesis. I am grateful that you offered this many-sided topic and gave me the opportunity to gain interesting insights into a practical field. Furthermore I want to express my gratitude to Hendrik Schreiber, BGR, for openly asking critical questions during the technical meetings that made me reconsider ideas for the model and pointed me in the right directions.

I am glad that it was possible to write this thesis within this close cooperation between the BGR and the Institute of Fluid Mechanics and Environmental Physics in Civil Engineering (ISU). Many thanks are dedicated to the colleagues from the BGR, that welcomed me and helped me with my questions. I especially want to thank Dr. Ing. Sara Vassolo for the various help, not least in finding available workstations at the office and Dr. Georg Houben, who agreed on being my second examiner.

I want to thank apl.-Prof. Dr. Thomas Graf from the ISU for facilitating this external master thesis as first examiner and taking the time for the numerous regular meetings, which were invaluable for both the progress and the process, and once for again asking the right questions to keep me reconsidering.

Special thanks go to the colleagues from the Agence du Bassin Hydraulique du Souss Massa (ABHSM), Ms Fatima Abourrig, Mr Amine Touab and Mr Baba Sy from the OSS, who greatly worked on the project and enabled insightful meetings.

At last, I want to thank my family and friends, who always gave me support during my studies.